Mathematical Formulation of Projection Problem

### 2024-09-23 docs/logbook.tex
Corrected objective function
Changed to float64, achieves slightly more spherical results

>>>>

	\begin{MeetingMinutes}{Fri 20/09/2024}{u7013004}
		Trying to add a regulariser between iterations for lower problem.
	\end{MeetingMinutes}

	\begin{MeetingMinutes}{Sun 22/09/2024}{u7013004}
		Going to fully do the regulariser and report results. Will also provide warm-starting with previous solution. 
	\end{MeetingMinutes}

	\begin{MeetingMinutes}{Mon 23/09/2024}{u7013004}
		Tried switching to float64 and it's not working. Going to try add more views. For 
	\end{MeetingMinutes}
